---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# textshaping

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/textshaping)](https://CRAN.R-project.org/package=textshaping)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![R-CMD-check](https://github.com/r-lib/textshaping/workflows/R-CMD-check/badge.svg)](https://github.com/r-lib/textshaping/actions)
<!-- badges: end -->

This package is a low level package that provides advanced text shaping capabilities to graphic devices. It is based on the [FriBidi](https://github.com/fribidi/fribidi) and [HarfBuzz](https://harfbuzz.github.io) libraries and provides full support for correctly shaping left-to-right, right-to-left, and bidirectional text with full support for all OpenType features such as ligatures, stylistic glyph substitutions, etc.

For an example of a package that uses textshaping to support advanced text layout see [ragg](https://ragg.r-lib.org).

A big thanks to [Behdad Esfahbod](http://behdad.org) who is the main author of both FriBidi and HarfBuzz and has been very helpful answering questions during the course of development.

## Installation
You can install textshaping from CRAN with `install.packages("textshaping")`. For the development version you can install it from Github with devtools:

```{r, eval=FALSE}
devtools::install_github("r-lib/textshaping")
```

Note that you will need both the development versions of FriBidi and HarfBuzz to successfully compile it.

## Code of Conduct
Please note that the textshaping project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
